\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
remove unused

\subsection{Experiment Result Analysis}
Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle condition, 18 \textmu s in stressed condition. And in the worse case, the latency is below 50 \textmu s. Meanwhile, the latency of PREEMPT\_RT has an averaged user-level latency more than 20 \textmu s, which means it can not guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 \textmu s in stressed condition).  As for mainline Linux, the max latency easily exceeds 1 ms. When comparing the performance of Xenomai 3 to Xenomai 2, we can see that the statistics in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.

\section{Conclusions}
We have evaluated the performance of two approaches to make Linux being real-time: PREEMPT\_RT and Xenomai, diversely presented in the view of single kernel and dual-kernel configurations on single-core ARM Cortex-A8, along with general conclusions about when each kernel configuration. As for the dual kernel configuration of Xenomai 3, latency is still significantly better, but PREEMPT\_RT shows closer performance at least for Linux kernel 3.14 stable release while it enables to run same application on different platforms and migrate existing POSIX application to Linux systems.

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though. It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter when the CPU is heavily loaded. This needs further investigation.

>>>>

\subsection{Experiment Result Analysis}
Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle condition, 18 \textmu s in stressed condition. And in the worse case, the latency is below 50 \textmu s. Meanwhile, the latency of PREEMPT\_RT has an averaged user-level latency more than 20 \textmu s, which means it can not guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 \textmu s in stressed condition).  As for mainline Linux, the max latency easily exceeds 1 ms. When comparing the performance between Xenomai 2 and Xenomai 3, we can see that the statistics in cyclictest and latency test would be slightly better, except for the case of timer-irq latency in stressed condition.

\section{Conclusions}
We have evaluated the performance of two approaches to make Linux being real-time: PREEMPT\_RT and Xenomai, diversely presented in the view of single kernel and dual-kernel configurations on single-core ARM Cortex-A8. As for the dual kernel configuration of Xenomai 3, latency is still significantly better, but PREEMPT\_RT shows closer performance at least for Linux kernel 3.14 stable release while it enables to run same application on different platforms and migrate existing POSIX application to Linux systems.

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2 in general. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though. It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter when the CPU is heavily loaded. This needs further investigation.
